### 2020-11-03 doc/manuscript/Dow_SI.Rmd
added climwin output figures to SI
had to copy over figures and rename (technical difficulties)

---
title: ''
author: ''
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
  html_document:
    df_print: paged
bibliography: null
biblio-style: apalike
csl: new-phytologist.csl
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}
---

@@

>>>>

---
title: ''
author: ''
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
  html_document:
    df_print: paged
bibliography: null
biblio-style: apalike
csl: new-phytologist.csl
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}
---
```{r eval = TRUE, echo=FALSE, warning=FALSE, results='hide'}
path_to_results <- paste0(dirname(dirname(getwd())), "/results/") #I was trying to read directly from results folder, but couldn't get it working.

# SUPPLEMENTARY INFO (copied from Dow_manuscript.Rmd)
#SI table numbers
sample_size_by_year= "S1"

#SI table captions
sample_size_by_year_caption <- "Table S1. Sample size by year"

#SI figure numbers
climwin_rp_DOY25_SCBI = "S1"
climwin_dp_DOY25_SCBI = "S2"
climwin_rp_DOY25_HARV = "S3"
climwin_dp_DOY25_HARV = "S4"
#SI figure captions
climwin_rp_DOY25_SCBI_short_caption <- "Figure S1. Full climwin output for DOY 25 for ring porous species at SCBI."
climwin_dp_DOY25_SCBI_short_caption <- "Figure S2. Full climwin output for DOY 25 for diffuse porous species at SCBI."
climwin_rp_DOY25_HARV_short_caption <- "Figure S3. Full climwin output for DOY 25 for ring porous species at Harvard Forest."
climwin_dp_DOY25_HARV_short_caption <- "Figure S4. Full climwin output for DOY 25 for diffuse porous species at Harvard Forest."

```

@@

\newpage

```{r climwin_rp_DOY25_SCBI, out.width="100%", echo=FALSE, fig.align="center", fig.cap= climwin_rp_DOY25_SCBI_short_caption}
knitr::include_graphics("tables_figures/SCBI_mettower_ring-porous_DOY25.png")
```

\newpage

```{r climwin_dp_DOY25_SCBI, out.width="100%", echo=FALSE, fig.align="center", fig.cap= climwin_dp_DOY25_SCBI_short_caption}
knitr::include_graphics("tables_figures/SCBI_mettower_diffuse-porous_DOY25.png")
```

\newpage

```{r climwin_rp_DOY25_HARV, out.width="100%", echo=FALSE, fig.align="center", fig.cap= climwin_rp_DOY25_HARV_short_caption}
knitr::include_graphics("tables_figures/HF_ring-porous_DOY25.png")
```

\newpage

```{r climwin_dp_DOY25_HARV, out.width="100%", echo=FALSE, fig.align="center", fig.cap= climwin_dp_DOY25_HARV_short_caption}
knitr::include_graphics("tables_figures/HF_diffuse-porous_DOY25.png")
```
